\bf Faster Neural Machine Translation Inference

### 2018-02-03 fast-beam/fast-beam.tex
fast beam paper

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. The sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which can increase batched inference speed by up to 41\% on modern GPUs without affecting model quality.

@@

There has been little work on batching algorithms, which is surprising considering its critical importance for fast model inference. ~\cite{Neubig-autobatching} describe an novel batching algorithm, however, its aim is to alleviate the burden on developers in batching of new models, not faster batching.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-europarl.png}} 
\end{tabular}
\caption{Translation speed for Europarl test set when using the fused kernel}
\label{fig:beam-europarl}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-opensubtitles.png}} 
\end{tabular}
\caption{Translation speed for Opensubtitles test set when using the fused kernel}
\label{fig:beam-opensubtitles}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Opensubtitles test set)}
\label{fig:pie-time-opensubtitles}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-europarl.png}} 
\end{tabular}
\caption{Translation speed for Europarl test set using top-up batching}
\label{fig:topup-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-opensubtitles.png}} 
\end{tabular}
\caption{Translation speed for OpenSubtitles test set using top-up batching}
\label{fig:topup-opensubtitles}
\end{figure}

@@

>>>>

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. The sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which can increase batched inference speed by up to 57\% on modern GPUs without affecting model quality.

@@

There has been surprisingly little work on batching algorithms, considering its critical importance for efficient deep-learning training and inference. ~\cite{Neubig-autobatching} describe an novel batching algorithm, however, its aim is to alleviate the burden on developers in batching of new models, not faster batching.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-europarl.png}} 
\end{tabular}
\caption{Speed using the fused kernel (Europarl)}
\label{fig:beam-europarl}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{beam-opensubtitles.png}} 
\end{tabular}
\caption{Speed using the fused kernel (Opensubtitles)}
\label{fig:beam-opensubtitles}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Opensubtitles)}
\label{fig:pie-time-opensubtitles}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-europarl.png}} 
\end{tabular}
\caption{Speed using top-up batching (Europarl)}
\label{fig:topup-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-opensubtitles.png}} 
\end{tabular}
\caption{Speed using top-up batching (OpenSubtitles)}
\label{fig:topup-opensubtitles}
\end{figure}

@@

\subsection{Cummulative Results}

Using both the fused kernel and top-up batching to translate
